---
title: "Question 1 and 2"
output: html_notebook
---

###Find out the Top 5 cities by performance (Higher CTR and Lower CPC. Impressions and Clicks should be reasonable.)

In order to solve this query sqldf library was used. Which helps in writting queries efficiently in R.

Assumptions made:

Best Cities by performance were measured by bestindicator which shows the ratio betwen impression got clicked and the cost associated with it.

Output:

Top 5 cities by performance are:

-Claxton

-Altha

-Port Hueneme

-Dover-Foxcroft

-York Beach

For Clicks:

1. Sum of Clicks= 0 were not considered reasonable

2. Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 

    1.000    1.000    1.000    2.844    2.000  190.000
  
3. Based on the click summary statistics, clicks>= mean were considered reasonable.   


```{r}
Data<-read.csv('D:/Rutgers Study Material/MultivariateData1.csv')
#Query:1
library(sqldf)
a<-sqldf('select City, Sum(Impressions) as Imp,Sum(Clicks) as Clk, Sum(Clicks * CPC) as totalcost, Sum(Clicks) * 1.000/Sum(impressions) as CTR, Sum(Clicks * CPC)/sum(Clicks) as TotalCPC, (Sum(Clicks) * 1.000/Sum(impressions))/(Sum(Clicks * CPC)/sum(Clicks)) as bestindicator  from Data  where impressions>=0 and Clicks>=0 group by City')
summary(a$Clk)
b<-sqldf('select City,clk,CTR,TotalCPC,bestindicator from a where clk>=2.844 group by City order by bestindicator desc')

head(b)
```

### Which Device has the highest and poorest performance ?

Assumptions made:

Performance of the device is measured by higher CTR and lower CPC with reasonable clicks and impression.

Output:

As per the 'bestindicator' we can say Roku performed the best but the impressions and clicks doesn't seem reasonable. 

Best device by performance: Mobile

Worst device by performance: Tablet

```{r}
#Query: 2
a<-sqldf('select DeviceType, Sum(Impressions) as Imp,Sum(Clicks) as Clk, Sum(Clicks * CPC) as totalcost, Sum(Clicks) * 1.000/Sum(impressions) as CTR, Sum(Clicks * CPC)/sum(Clicks) as TotalCPC, (Sum(Clicks) * 1.000/Sum(impressions))/(Sum(Clicks * CPC)/sum(Clicks)) as bestindicator  from Data  where impressions>=0 and Clicks>=0 group by DeviceType')
b<-sqldf('select DeviceType,clk,CTR,TotalCPC,bestindicator from a group by DeviceType order by bestindicator desc')
head(b)
```




